A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-22 main.tex
Writing a decsription of QPercent.

The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
\QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns, \QCsp\ are generated directly from the syntax of a term.
\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
\QTBLTB and \QLambda are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.

% \QCspの説明

>>>>

The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
\QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns, \QCsp\ are generated directly from the syntax of a term.
\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
\QTBLTB and \QLambda\ are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.

% \QPercentの説明
The rule \QPercent is something special because it has no background of syntax or reductions.
But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
For example, we can utilize a dependently typed multistage calculus to generate a code for matrix multiplication.
When we know sizes of matrices before the multiplication,
we can generate efficient code for multiplication by unrolling loops.
